Probabilistic Forecasting of Geomagnetic Indices using Gaussian Process Models

### 2017-04-07 chap.tex
CSA: Section Complete

>>>>

To illustrate how CSA updates are made and accepted consider a population or ensemble of hyper-parameter values ${x_i}$ which can be considered to be initialised in a grid based fashion. For each configuration $x_i$ a probing solution $y_i = x_i + \epsilon$ is generated where $\epsilon$ is drawn from some random variable. The acceptance probability of the solution is calculated as shown below.

\begin{align*}
\mathbb{P}(x_i \rightarrow y_i | {x_i}) & = \frac{exp(-E(y_i)/T)}{exp(-E(y_i)/T) + \gamma} \\
\gamma & = \sum_{j}{exp \left ( \frac{-E(x_j)}{T} \right )}
\end{align*}

The quantity $\gamma$ defines the \emph{coupling} between the states ${x_i}$ of the ensemble, when the number of configurations in the emsemble $x_i$ is one this rule reduces to the classical \emph{Metropolis-Hastings} acceptance rule of the SA algorithm. Upto 4 variants of the CSA algorithm have been defined with different acceptance rules and temperature annealing schedules, the reader is advised to refer to \citet{Xavier-De-Souza2010} for an in-depth treatment of the CSA optimization class.
